HEP Software Foundation Community White Paper Working Group -- Training, Staffing and Careers

### 2018-06-14 CWP/papers/HSF-CWP-2017-02_training/latex/cwp-wg-training-careers.tex
Some more challenges.

Within a single experiment, different skill sets are needed. In addition to a
skill set that contains basic programming language knowledge, testing and code
management tools, and experiment-specific framework knowledge, there are more
specialized skills that only a subset of the community needs to know, such as
software optimization, or low-level hardware interfaces.
While there already are experiment-specific training efforts in place, there are
many needs that are in common between experiments. Therefore, we should probably
strive to extract the common knowledge and build a common training program. This
would reduce duplication of efforts and enable growth of a shared training
culture by accumulating and sharing expertise across different experiments.

To realise this goal, a possibility could be the institution of a {\em
federation} of existing training initiatives, a very lightwheight umbrella just
aimed at improving the efficiency and cost-effectivness of this important
activity.

\section{Implementation Roadmap}
The implementation of training should target multiple training formats and knowledge transfer, such as videos, wikis, lectures, jupyter notebooks and advanced visualizations, etc.
People who learn in non-conventional ways should not be excluded from the
opportunity to learn. Since there are different stages of knowledge transfer,
programs should be developed that encourage experts to share knowledge. Issues
considered in this section include global training initiatives, strategies for
leveraging existing forums, and training tool development.

@@

In the context of web-based training, if HSF helps to constitute a living
collection of online tutorials, we could organize regular events such as
a "Tutorial of the month", based on students votes. From a more general point
of view, since the publications are the most universal recognized items
in the research community, we should try hardly to create some sort of
training journal, with reviewed training papers.

>>>>

Within a single experiment, different skill sets are needed. In addition to a
skill set that contains basic programming language knowledge, testing and code
management tools, and experiment-specific framework knowledge, there are more
specialized skills that only a subset of the community needs to know, such as
software optimization, or low-level hardware interfaces.
While there already are experiment-specific training efforts in place, there are
many needs that are in common between experiments. Therefore, we should probably
strive to extract the common knowledge and build a common training program. This
would reduce duplication of efforts and enable growth of a shared training
culture by accumulating and sharing expertise across different experiments.
To realise this goal, a possibility could be the institution of a {\em
federation} of existing training initiatives, a very lightwheight umbrella just
aimed at improving the efficiency and cost-effectivness of this important
activity.

Yet, when trying to exchange training materials within a group, the problem
is not only to convince authors to give their work. This first resistance
can be facilitated with cautious intellectual property clauses. The other
problem is that trainers do not like to reuse a given material as-is. They usually
absolute want to refactor it, so to build their own training story.
Thus, it is really difficult to have everyone agrees on common material.
It is even challenging to have them all host their material in the same
centralized place. A way to bypass this could be to settle for a centralized
catalog, each author being free to host his material in his favorite place.

Another challenge, as already stated, is the wide heterogeneity of the
competences of the students. A special care must be given to setup
training structure that can cope with both beginners and advanced students.
This may rely on a low granularity subdivision of independant topics.
The IN2P3 authors try to restrain their tutorials within a 20 minutes
time frame, as inspired by the Pomodoro technique, so that one can easily jump
and compose his own menu. But it turns to be tricky to keep such small
tutorials really independant and meaningful when one choose them at will.

Last but not least, any trainer has faced the tremendous lost of time
with the softare installation step, at the beginning of any session, when
many students have unhappilly not prepared their machine in advance,
despites repeated injonctions... Here the containers may bring a real
progress, provided everyone have at least Docker installed on his machine.
JupyterHub, also, is a technology which enable training session with
no need for installation (but need for network).

%____________________________________________________________________
%____________________________________________________________________
\section{Implementation Roadmap}
The implementation of training should target multiple training formats and knowledge transfer, such as videos, wikis, lectures, jupyter notebooks and advanced visualizations, etc.
People who learn in non-conventional ways should not be excluded from the
opportunity to learn. Since there are different stages of knowledge transfer,
programs should be developed that encourage experts to share knowledge. Issues
considered in this section include global training initiatives, strategies for
leveraging existing forums, and training tool development.

@@
